APPM report - Draft

### 2022-10-10 paper_version/main.tex
remove insertion of missing figures
fix errors
minor change
polish 2.1 introduction on AP

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}

@@

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zea \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}\mathbf{n_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{e_*} \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Maxwell equations:}
    \begin{align*}
    \varphi &= \varphi^i(t)\ \ \text{on} \ \ \Gamma_C^i, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\subsection{1D Discretization}
In this section we briefly discuss the underlying work \cite{degond_2012} on which our work is built. Meanwhile, this section also serves as a preliminary case study such that readers can better understand the 3D scheme that we present. 
\subsubsection{1D plasma model}
The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig. \ref{fig:1d-frame} for the definition of reference frame). Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The collision between particles is omitted for the time being. 
\begin{figure}
    \centering
    \includegraphics[scale=0.2]{1d_frame.png}
    \caption{Projection of the 3D model onto $z$-axis. Let us consider a Cartesian mesh doublet. The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis. Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
    \label{fig:1d-frame}
\end{figure}

@@

\subsection{Reduction to 1D case}
On enforcing the traverse invariance, the 3D discretization boils down to the 1D case, which provides a justification of our implementation.
The Euler-Maxwell system at the axis of symmetry is formulated as 
\begin{align}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align}
Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified. We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model. With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig. \ref{fig:z_axis_reduction}.
\begin{figure}
    \centering
    \includegraphics{z_axis_reduction.eps}
    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model. The results are both generated on meshes with 64 cells along $z$-axis. No friction term exists. $t = 5 \times 10^{-4}.$}
    \label{fig:z_axis_reduction}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.4]{primal_mesh.png}
    \hspace{2cm}
    \includegraphics[scale=0.4]{dual_mesh.png}
    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
    \label{fig:primal_dual_meshes}
\end{figure}

@@

In Fig. \ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization. First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results. In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field. The electrons move in the inverse direction of the electric field. Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case. For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$. Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
\begin{figure}
    \centering
    \includegraphics[scale=0.35]{E_lambda_1.png}
    \includegraphics[scale=0.35]{B_lambda_1.png}
    \includegraphics[scale=0.35]{ue_lambda_1.png} \\
    (a) $\lambda = 1.0$ \\
    \includegraphics[scale=0.35]{E_lambda_1e-2.png}
    \includegraphics[scale=0.35]{B_lambda_1e-2.png}
    \includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
    (b) $\lambda = 0.01$ \\
    \includegraphics[scale=0.35]{E_lambda_0.png}
    \includegraphics[scale=0.35]{B_lambda_0.png}
    \includegraphics[scale=0.35]{ue_lambda_0.png} \\
    (c) $\lambda = 0$
    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
    \label{fig:grid_study_3d}
\end{figure}

@@

    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
    \includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-1e-1}
\end{figure}

@@

    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
    \includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-0}
\end{figure}

To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig. \ref{fig:origin-data_vs_time}. Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time. In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state. It is a reflection of the shielding effect of plasma which is characterized by the Debye length. It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia. Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
\begin{figure}
    \centering
    \includegraphics[scale=0.9]{origin-data_vs_time.eps}
    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
    \label{fig:origin-data_vs_time}
\end{figure}

A critical sign of quasi-neutrality is the vanishing charge. In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied. To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig. \ref{fig:zaxis-data_vs_z-T_10}. The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$. Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
\begin{figure}
    \centering
    \includegraphics{zaxis-data_vs_z-T_10.eps}
    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
    \label{fig:zaxis-data_vs_z-T_10}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{subcaption}

@@

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Maxwell equations:}
    \begin{align*}
    \varphi &= \varphi^i(t)\ \ \text{on} \ \ \Gamma_C^i, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\subsection{Asymptotic-Preserving schemes}
As is mentioned in the proceeding chapter, the zero-Debye-length limit poses a singularly perturbed problem in the sense that the Maxwell-Euler equations changes its type from a hyperbolic to hyperbolic-elliptic one. To simulate a plasma, one usually first identifies which regime it lies in and designs the scheme according to its type. Nonetheless, there exist cases that covers both regimes and cannot be approximated by either of them. Due to the difference on their mathematical characters, naively applying classical schemes for $\lambda = \mathcal{O}(1)$ to problems with $\lambda \rightarrow 0$ would fail and vice versa. \emph{Asymptotic-preserving} (AP) schemes are such a class of schemes that provide a unified approach for both limit and non-limit problems.

To illustrate the general concept of AP schemes, we quote the celebrated commutative diagram Fig. \ref{fig:commutative_diagram_ap} in \cite{jin_1999} which sketches the property that an AP scheme should possess. We consider a parametrized problem $P^\lambda$ that converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$. To discretize $P^\lambda$, the scheme $P^\lambda_h$ is constructed whose numerical results depend on some discretization parameter $h$, e.g. mesh size. Beside the convergence of the scheme $P^\lambda_h$ to its analytic solution $P^\lambda$ as $h\rightarrow0$, the AP property additionally requires that the convergence of $P^\lambda_h$ to the limit discrete model $P^0_h$ as $\lambda\rightarrow0$. Such a limit scheme $P^0_h$ should in turn converge to the continuous solution $P^0$ as $h \rightarrow 0$. In short, an AP scheme $P^\lambda_h$ makes the diagram Fig. \ref{fig:commutative_diagram_ap} commutative.

The concept of AP schemes can be traced back to \cite{jin_1995} in which the authors approximate a conservation law by a hyperbolic system with relaxation, and manage to construct a scheme that is stable for an arbitrarily small relaxation parameter. The term ``asymptotic-preserving" was formally introduced in \cite{jin_1999} for handling the diffusive regime of kinetic models. This concept stemmed from and remains very active in kinetic models with stiff relaxations, see \cite{jin_2010} and the references therein. Nonetheless, considerable effort has been put into developing AP schemes for many other problems that admit asymptotic behavior. For instance, in fluid dynamics, the so-called \emph{all-speed} schemes are advantageous when dealing with both compressible and incompressible regimes simultaneously. \cite{degond_2007, haack_2010} devise all-speed schemes for the isentropic Euler equations through fast-slow decomposition of velocity fields. Concerning plasma physics, a number of papers are available dealing with the quasi-neutral limit of the Euler-Poisson (or Euler-Maxwell) system \citep{crispel_2005, degond_2008, degond_2011, degond_2012} and Vlasov-Poisson (or Vlasov-Maxwell) system \citep{degond_2017, degond2017b, zhu_2017}. Besides, \cite{caflisch_1997, berthon2011} concern AP schemes for generic hyperbolic systems with relaxation source terms. For a comprehensive review on AP schemes, readers are referred to \cite{jin_2010} for kinetic and hyperbolic equations, and \cite{degond_2017} for multiscale plasma simulations.

To devise an AP scheme, the dependence of the stability constraints of $h$ on $\lambda$ has to be removed. This is mainly achieved by utilizing implicit time-stepping for certain terms. As is summarized by \cite{degond_2017}, AP schemes aim to bridge several sets of equations describing the system in different regimes, rather than to alleviate the stability constraints of the numerical methods. In this sense, a fully-implicit scheme is likely to be overkill and thus a smart construction is necessary. The second consideration goes to the identification of a compatible boundary conditions for both regimes, which would be shown to be essential for the numerical stability.

In the following sections, we first briefly discuss the 1D scheme for the Maxwell-Euler system devised by \cite{degond_2012} on which our work us built. this section also serves as a preliminary case study such that readers can better understand the 3D scheme.

\begin{figure}
    \centering
    \begin{tikzpicture}
    \node (nw) {\Large $P^\lambda_h$};
    \node (ne) [right=3cm of nw]{\Large $P^\lambda$};
    \node (sw) [below=of nw]{\Large $P^0_h$};
    \node (se) [right=3cm of sw]{\Large $P^0$};
    \draw[->] (nw.east)  -- node [above,midway] {$h\rightarrow0$} (ne.west) ;
    \draw[->] (nw.east)  --  (ne.west) ;
    \draw[->] (nw.south) -- node [left,midway] {$\lambda\rightarrow0$} (sw.north);
    \draw[->] (nw.south) -- node {} (sw.north);
    \draw[->] (sw.east)  -- node [above,midway] {$h\rightarrow0$}(se.west);
    \draw[->] (ne.south) -- node [left,midway] {$\lambda\rightarrow0$} (se.north);
    \end{tikzpicture}
    \caption{Commuting diagram of AP schemes}
    \label{fig:commutative_diagram_ap}
\end{figure}

\colorbox{red}{Polish until here.}

\subsection{1D Discretization}
\subsubsection{1D plasma model}
The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig. \ref{fig:1d-frame} for the definition of reference frame). Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The collision between particles is omitted for the time being. 
\begin{figure}
    \centering
    %\includegraphics[scale=0.2]{1d_frame.png}
    \caption{Projection of the 3D model onto $z$-axis. Let us consider a Cartesian mesh doublet. The reduction is accomplished by assigning the quantities defined on each cross-section, which is parallel to the $x$-$y$ plane, to its intersection point at $z$-axis. Since it is assumed that no variations occur in each cross-section, the quantities in 3D can be compressed by the ones that locate at each mesh point on the $z$-axis.}
    \label{fig:1d-frame}
\end{figure}

@@

\subsection{Reduction to 1D case}
On enforcing the traverse invariance, the 3D discretization boils down to the 1D case, which provides a justification of our implementation.
The Euler-Maxwell system at the axis of symmetry is formulated as 
\begin{align}
    &\partial_t n_* + \partial_z(n_*u_{*,z}) = 0, \\
    &\partial_t (n_* u_{*,z}) + \partial_z(n_*u_{*,z}^2) + \varepsilon_*^{-2} \partial_z P_* = \varepsilon_*^{-2}q_*n_*E_z, \\
    &\partial_t (n_*e_*) + \partial_z (n_* h_* u_{*,z}) = \varepsilon_*^{-2} q_* n_* u_{*,z} E_z, \\
    \lambda^2 &\partial_t E_z = \sum_* - q_* n_* u_{*,z}.
\end{align}
Recall that in section \ref{sec:two_fluid_model} the two-fluid model in 1D setting is discussed and verified. We take the results as reference solutions for the 1D reduction on the $z$-axis of the 3D model. With the same setting as is described in section \ref{sec:1d_two_fluid_numerical_results} and the vanishing anode potentials, we expect the results produced by the purely 1D model and 1D reduction of the 3D model to behave in a similar way, which is shown in Fig. \ref{fig:z_axis_reduction}.
\begin{figure}
    \centering
    %\includegraphics{z_axis_reduction.eps}
    \caption{Comparison of 1D two-fluid model and reduced 1D model on $z$-axis from 3D two-fluid model. The results are both generated on meshes with 64 cells along $z$-axis. No friction term exists. $t = 5 \times 10^{-4}.$}
    \label{fig:z_axis_reduction}
\end{figure}

@@

\begin{figure}
    \centering
    %\includegraphics[scale=0.4]{primal_mesh.png}
    \hspace{2cm}
    %\includegraphics[scale=0.4]{dual_mesh.png}
    \caption{Primal (left) and dual (right) meshes used for the 3D testing case. They are generated by the code developed in \cite{fuchs_2021}.}
    \label{fig:primal_dual_meshes}
\end{figure}

@@

In Fig. \ref{fig:3d_vec_field_E_B_ue} we present the vector fields of the numerical solutions for $\lambda = 1.0, 0.01, 0$ at $t = 0.1$, aiming to give an intuitive visualization. First of all, one \emph{a priori} expects the rotational symmetry in the solutions, which serves as a basic criterion to justify the results. In terms of the 3D structure of the electromagnetic fields, the electric field points from the anode to the cathode, and the magnetic field is spiral-shaped and orthogonal to the electric field. The electrons move in the inverse direction of the electric field. Regarding the asymptotic behavior of the AP scheme, the primary concern is its validity in the limiting case. For this case, the scheme manages to produce a meaningful numerical solution when $\lambda = 0$. Besides, by comparing the solutions for different $\lambda$, the smooth transition from the non-neutrality to quasi-neutrality is observed, which is an implication that the scheme reproduces the asymptotic behavior of the analytical solutions from the non-neutral model to the quasi-neutral one.
\begin{figure}
    \centering
    %\includegraphics[scale=0.35]{E_lambda_1.png}
    %\includegraphics[scale=0.35]{B_lambda_1.png}
    %\includegraphics[scale=0.35]{ue_lambda_1.png} \\
    (a) $\lambda = 1.0$ \\
    %\includegraphics[scale=0.35]{E_lambda_1e-2.png}
    %\includegraphics[scale=0.35]{B_lambda_1e-2.png}
    %\includegraphics[scale=0.35]{ue_lambda_1e-2.png} \\
    (b) $\lambda = 0.01$ \\
    %\includegraphics[scale=0.35]{E_lambda_0.png}
    %\includegraphics[scale=0.35]{B_lambda_0.png}
    %\includegraphics[scale=0.35]{ue_lambda_0.png} \\
    (c) $\lambda = 0$
    \caption{Snapshots of the $\mathbf{E}$-field, $\mathbf{B}$-field, and $\mathbf{u}_e$ for different $\lambda$ at $t = 10$ based on a primal mesh with 1920 cells (8 cells along $z$-axis). } 
    \label{fig:3d_vec_field_E_B_ue}
\end{figure}

@@

\begin{figure}
    \centering
    %\includegraphics[scale=0.9]{norm_vs_nCell-T_1.eps}
    \caption{1-norms of quantities with respect to different mesh size: The results are computed for $\lambda = 1$ and $0.1$ at $t = 1$.}.
    \label{fig:grid_study_3d}
\end{figure}

@@

    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_8-2-2.png}
    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_16-3-3.png}
    %\includegraphics[scale=0.27]{clip_E_T-1_lambda-1e-1_32-3-4.png}
    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_8-2-2.png}
    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_16-3-3.png}
    %\includegraphics[scale=0.27]{clip_B_T-1_lambda-1e-1_32-3-4.png}
    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_8-2-2.png}
    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_16-3-3.png}
    %\includegraphics[scale=0.27]{clip_ne_T-1_lambda-1e-1_32-3-4.png}
    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_8-2-2.png}
    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_16-3-3.png}
    %\includegraphics[scale=0.27]{clip_ni_T-1_lambda-1e-1_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0.1$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-1e-1}
\end{figure}

@@

    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_8-2-2.png}
    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_16-3-3.png}
    %\includegraphics[scale=0.27]{slice_E_T-1_lambda-0_32-3-4.png}
    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_8-2-2.png}
    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_16-3-3.png}
    %\includegraphics[scale=0.27]{slice_B_T-1_lambda-0_32-3-4.png}
    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_8-2-2.png}
    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_16-3-3.png}
    %\includegraphics[scale=0.27]{slice_ne_T-1_lambda-0_32-3-4.png}
    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_8-2-2.png}
    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_16-3-3.png}
    %\includegraphics[scale=0.27]{slice_ni_T-1_lambda-0_32-3-4.png}
    \caption{Quantities at the cross-section generated by meshes with different refinement level. Refinement 1: 1920 primal cells; Refinement 2: 14592 primal cells; Refinement 3: 30720 primal cells. The snapshots are computed for $\lambda = 0$ at $t = 1$.}
    \label{fig:grid_study_3d_clip_lambda-0}
\end{figure}

To inspect how the system evolves, we extract the time histories of certain quantities at the origin (the center of the tube) up to $t = 10$ and display them in Fig. \ref{fig:origin-data_vs_time}. Being originally at rest, the system is excited by the suddenly applied voltage and generates oscillations that dampen over time. In general, a large value of $\lambda$ leads to stronger oscillations with larger amplitude whereas smaller $\lambda$ incurs more damping and the system rapidly reaches a steady state. It is a reflection of the shielding effect of plasma which is characterized by the Debye length. It can also be noticed that the electron velocity becomes steady much sooner than ion velocity, which is a consequence of the huge difference in inertia. Besides, the convergence of the discrete model as $\lambda \rightarrow 0$ can be observed---the solution becomes steady over time.
\begin{figure}
    \centering
    %\includegraphics[scale=0.9]{origin-data_vs_time.eps}
    \caption{Time histories of quantities at the origin for different $\lambda$. The simulation is done on a mesh with 1920 primal cells with 8 layers along $z$-axis.}
    \label{fig:origin-data_vs_time}
\end{figure}

A critical sign of quasi-neutrality is the vanishing charge. In fact, in Section \ref{sec:quasi-neutral_limit} we discuss the limiting model where $\rho = 0$ is satisfied. To examine that, the quantities at the $z$-axis over different $\lambda$ are provided in Fig. \ref{fig:zaxis-data_vs_z-T_10}. The right figure demonstrates the approaching and eventual coincidence of electron and ion densities as $\lambda \rightarrow 0$. Furthermore, with relatively small but non-zero $\lambda$, the bulk of the plasma is approximately neutral while the area near the electrodes is not, which is known as a plasma sheath and within such an area the quasi-neutrality is usually inappropriate.
\begin{figure}
    \centering
    %\includegraphics{zaxis-data_vs_z-T_10.eps}
    \caption{Quantities along $z$-axis for different $\lambda$: The results are computed at $t = 10$ on a mesh with 1920 primal cells with 8 layers along $z$-axis.}.
    \label{fig:zaxis-data_vs_z-T_10}
\end{figure}
